---
title: "Pair Quiz"
author: "Cabanayan, Cantal, San Luis"
date: "7/29/2021"
output: html_document
---

```{r setup, include=FALSE}
library(scatterplot3d)
knitr::opts_chunk$set(echo = TRUE)
```

# Question 2

### An article in Optical Engineering ["Operating Curve Extraction of a Correlator's Filter" (2004, Vol. 43, pp. 2775-2779)] reported on the use of an optical correlator to perform an experiment by varying brightness and contrast. The resulting modulation is characterized by the useful range of gray levels. The data follow:
  
  
```{r, echo=FALSE}
usefulrange <- c(96, 50, 50, 112,	96,	80,	155, 144,	255)
brightness <- c(54, 61, 65, 100,	100,	100,	50,	57,	54)
contrast <- c(56,	80,	70,	50,	65,	80,	25,	35,	26)

correlator.data <- data.frame(
 usefulrange = c(96, 50, 50, 112,	96,	80,	155, 144,	255),
 brightness = c(54, 61, 65, 100,	100,	100,	50,	57,	54),
 contrast = c(56,	80,	70,	50,	65,	80,	25,	35,	26))
 correlator.data
```

  
```{r}
s3d <- scatterplot3d(brightness, contrast, usefulrange, type = "h", color = "blue", angle=30, pch = 16)

multiple.regression <- lm(usefulrange ~ brightness + contrast, data=correlator.data)

s3d$plane3d(multiple.regression, lty.box = "solid")

summary(multiple.regression)
```
  
  
#### A. Fit a multiple linear regression model to these data.

Formula for multiple linear regression model:

$$ y = \beta_0 + \beta_1 X_1 + \beta_2 X_2$$
**where**

**$y$ = Useful range (ng)**  
**$\beta_0$ = y-intercept**  
**$\beta_1$ =  slope 1**
**$\beta_2$ =  slope 2**
**$X_1$ = Brightness (%)**  
**$X_2$ = Contrast (%)**  

Inputting the values solved by our code chunk,

$$ y = 238.56 + 0.3339 X_1 + (-2.7167) X_2
\\ 
\\
y = 238.56 + 0.3339 X_1 -2.7167 X_2$$

#### B. Estimate $\sigma^2$.

```{r}
(summary(multiple.regression)$sigma)**2
```


#### C. Compute the standard errors of the regression coefficients.

As seen from the results by our code chunk,

$$ SE(\beta_0)=  45.2285
\\
SE(\beta_1)= 0.6763
\\
SE(\beta_2)= 0.6887$$

#### D. Predict the useful range when brightness= 80 and contrast= 75.
 
 We will use our multiple regression model and will be inputting our values knowing that $X_1$ = 80 and $X_2$ = 75.
 
 $$ y = 238.56 + 0.3339 X_1 - 2.7167 X_2 
 \\
 = 238.56 + 0.3339(80) - 2.7167(75)
 \\
 y = 61.5195 $$
  
#### E. Test for significance of regression using $\alpha=0.05$. What is the $P$-value for this test?

The test for significance of regression is used to determine if a linear relationship exists between the response variable $y$ and the subset of regressor variables $x_1, x_2$.

The hypotheses are:

**Null Hypothesis** $H_0: \beta_1 = \beta_2 = 0$ 

**Alternative Hypothesis** $H_1: \beta_j \neq 0$ for at least one $j$

Rejection of the null hypothesis implies that at least one of the regressor variables contributes greatly to the regression model.

As seen in our code chunk, the $P$-value for this test is $0.01459$. As we should know, if the $P$-value for a variable is less than our significance level, we have enough evidence to reject our null hypothesis. Since we are given the significance level $\alpha=0.05$, 

$$0.01459 < 0.05$$

Since the $P$-value is less that $\alpha$, the null hypothesis is rejected. Therefore, at least one of the variables is significant to the model.

#### F. Construct a t-test on each regression coefficient. What conclusions can you draw about the variables in this model? Use $\alpha = 0.05$.

The $t$-test is used to check the significance of each regression coefficient in the multiple linear regression model. The hypotheses for this test are:

**Null Hypothesis** $H_0: \beta_j = 0$ 

The tested regression coefficient is not significant to the regression model.

**Alternative Hypothesis** $H_1: \beta_j \neq 0$

The tested regression coefficient is significant to the regression model.

<br>
<br>

From the summary of the regression model, the $t$-value for each regression coefficient is given:

For $\beta_1$ or "brightness," $t_0 = 0.494$

For $\beta_2$ or "contrast," $t_0 = -3.945$

The degrees of freedom for the $t$-value is given as $n - p$, where $n$ is the number of samples and $p$ is the number of parameters given.

$n = 9, p = 3$, giving us a degree of freedom of $6$.

*The null hypothesis is rejected if $|t_0| > t_{\alpha/2, n - p}$*

```{R}

qt(0.025, 6, lower.tail = F)

```

$$
|(t_0)_{\hat{\beta}_1}| = 0.494 \ngtr 2.446912
\\
|(t_0)_{\hat{\beta}_2}| = 3.945 > 2.446912
$$

From the $t$-test for significance for $\beta_1$, there is not enough evidence to reject the null hypothesis. Therefore, the "brightness" variable is not significant to the regression model.

For the significance for $\beta_2$, there is enough evidence to reject the null hypothesis. Therefore, the "contrast" variable is significant to the regression model.
